---
title: "ST558: Homework 4 - Hodge Podge"
author: "Lamia Benyamine"
description: "Creating functions and querying an API"
date: "June 25, 2024"
format: html
editor: visual
---

# *Task 1:* Conceptual Questions

1.  What is the purpose of the lapply() function? What is the equivalent purrr function?

-   lapply() applies a function to every element of a list. In the purr package, the map() function is the equivalent to lapply().

2.  Suppose we have a list called my_list. Each element of the list is a numeric data frame (all columns are numeric). We want use lapply() to run the code cor(numeric_matrix, method = "kendall") on each element of the list. Write code to do this below! (I’m really trying to ask you how you specify method = "kendall" when calling lapply())

-   lapply(X = my_list, FUN = cor, method = "kendall")

3.  What are two advantages of using purrr functions instead of the BaseR apply family?

-   Like most tidyverse functions, purr functions are a more consistent way to apply functions to objects and there are many more helper functions available.

4.  What is a side-effect function?

-   A side-effects are pipeable functions that return the original data instead of the transformed data from previous steps.

5.  Why can you name a variable sd in a function and not cause any issues with the sd function?

-   R will look up the name depending on the context if it is a call R will look for a function, if it is a name, R will look for an object.

# *Task 2:* Writing R Functions

## RMSE

Create a function that takes in a vector of responses and predictions and outputs the Root Mean Square Error (RMSE).

```{r RMSE function}
getRMSE <- function(response, prediction, ...) {
  rmse <- sqrt(mean((response - prediction)^2, ...))
  return(rmse)
}
```

Test RMSE function.

```{r RMSE test}
#Use provided random seed generation
set.seed(10)
n <- 100
x <- runif(n)
resp <- 3 + 10*x + rnorm(n)
pred <- predict(lm(resp ~ x), data.frame(x))

#Test 1 - default
getRMSE(resp, pred)

##Replace two response values with missing values
resp <- replace(resp, 99:100, NA_real_)

#Test 2 - do not specify what to do with NA
getRMSE(resp, pred)

#Test 3 - specify to remove NA values
getRMSE(resp, pred, na.rm = TRUE)
```

## MAE

Create a function that takes in a vector of responses and predictions and outputs the Mean Absolute Error (MAE).

```{r MAE function}
getMAE <- function(response, prediction, ...) {
  mae <- mean(abs(response - prediction), ...)
  return(mae)
}
```

Test MAE function.

```{r MAE test}
#Use provided random seed generation
set.seed(10)
n <- 100
x <- runif(n)
resp <- 3 + 10*x + rnorm(n)
pred <- predict(lm(resp ~ x), data.frame(x))

#Test 1 - default
getMAE(resp,pred)

##Replace two response values with missing values
resp <- replace(resp, 99:100, NA_real_)

#Test 2 - do not specify what to do with NA
getMAE(resp, pred)

#Test 3 - specify to remove NA values
getMAE(resp, pred, na.rm = TRUE)
```

## Wrapper

Create a function that can be used to calculate either or both RSME and MAE with a single call. Add conditions if the data is not a numeric atomic vector. Also add condition to check the metric is correct.

```{r Wrapper function}
getMetric <- function(response, prediction, metric = "both", ...) {
  if (!is.numeric(response) || !is.vector(response) || !is.atomic(response)) {
    warning("response argument is not numeric, vector, or atomic: returning NA")
    return(NA_real_)
    stop()
  }
  if (!is.numeric(prediction) || !is.vector(prediction) || !is.atomic(prediction)) {
    warning("prediction argument is not numeric, vector, or atomic: returning NA")
    return(NA_real_)
    stop()
  }
  if (metric == "both") {
    rmse_value <- getRMSE(response, prediction, ...)
    mae_value <- getMAE(response, prediction, ...)
    return(list(rmse_value = rmse_value, mae_value = mae_value)) #use a named list
  } else if (metric == "mae") {
    mae_value <- getMAE(response, prediction)
    return (mae_value = mae_value, ...)
  } else if (metric == "rmse") {
    rmse_value <- getRMSE(response, prediction)
    return (rmse_value = rmse_value, ...)
  } else {
    print("please input a valid metric: both, rsme, or mae. returning NA")
    return(NA_real_)
    stop()
  }
}
```

Test Wrapper function.

```{r Wrapper test}
#Use provided random seed generation
set.seed(10)
n <- 100
x <- runif(n)
resp <- 3 + 10*x + rnorm(n)
pred <- predict(lm(resp ~ x), data.frame(x))

#Test 1 - default returns both metrics
getMetric(resp, pred)

#Test 2 - only return MAE
getMetric(resp, pred, metric = "mae")

#Test 3 - only return RMSE
getMetric(resp, pred, metric = "rmse")

#Replace two response values with missing values
resp <- replace(resp, 99:100, NA_real_)

#Test 4 - do not specify what to do with NA
getMetric(resp, pred)

#Test 5 - specify to remove NA values
getMetric(resp, pred, na.rm = TRUE)

#Test 6 - pass incorrect data
getMetric(letters[1:12], pred) #incorrect vector type

getMetric(resp,pred, na.rm = True, metric = "mean") #incorrect metric type
```

# *Task 3:* Querying an API and Tidy-Style Function

Connect to the news api and select a topic of choice.

```{r connect api}
library(jsonlite)
library(dplyr)
url_id <- "https://newsapi.org/v2/everything?q=tesla&from=2024-05-25&sortBy=publishedAt&apiKey=6c4722dace224f01b1762cd4b8cd2165"
id_info <- httr::GET(url_id)

str(id_info,max.level = 1)

parsed <- fromJSON(rawToChar(id_info$content))
info <- as_tibble(parsed$articles) |>
  collect() |>
 filter(title == "Mycocycle uses mushrooms to upcycle old tires and construction waste | TechCrunch")
info
```

Write a function that allows a user to query this API and select the news title and date range

```{r api function}

```
